Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
correct standardization, weighting, and ordinalization for DGECriteriaN
first regressions with factors
ghjk
hjzuiu

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
library(stargazer)
library(cowplot)
@

@@

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")

stargazer(lm_ms, lm_ts, title = "Regression outcome: Grants", align = TRUE)  
@
<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=

@@

stargazer(lm_lDGE, lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
@
<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=

@@

\begin{equation}
\label{ModelProdu}
\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

>>>>

<<LoadingPackages, include=FALSE>>=
library(knitr)
library(xtable)
library(dplyr)
library(stargazer)
library(cowplot)
library(texreg)
@

@@

lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
#outlier meals
#outlier trips 
#impute meals
#imputetrips

stargazer(list(lm_ms, lm_ts), title = "Regression outcome: Grants", align = TRUE)  
@

<<Health Regressions Scatterplots, echo=FALSE, results='asis', message=FALSE>>=
Health_plots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_plots.Rds")
print(Health_plots)
@

<<Health Regressions percentageplots, echo=FALSE, results='asis', message=FALSE>>=
Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
print(Health_percentageplots)
@

<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=

@@

stargazer(lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
@
<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=

@@

\begin{equation}
\label{ModelProdu}
\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}
